---
title: "consonant_assimilation_data"
author: Alexander Volkmann
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{consonant_assimilation_data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(data.table)
library(funData)
library(gridExtra)
library(multifamm)
library(multifammPaper)
library(stargazer)
library(tidyverse)
library(viridis)
data(phonetic)
```

# Analysis of the Consonant Assimilation Data

This vignette provides the code to reproduce the analysis of the consonant assimilation data presented in the paper "Multivariate functional additive mixed models" (Volkmann et al., 2021). Note that this vignette does not execute the presented code because the required computing resources can be large.

## Plot the Data

```{r}
RNGkind(sample.kind = "Rounding")
set.seed(1234)
chosen_0 <- sample(unique(subset(phonetic, covariate.1 == 0)$n_long),
                   size = 3)
chosen_1 <- sample(unique(subset(phonetic, covariate.1 == 1)$n_long),
                   size = 3)

# Prepare data for plotting
dat <- copy(phonetic)
dat$color <- factor(dat$n_long*(dat$n_long %in% c(chosen_0, chosen_1)),
                    levels = c(0, chosen_0, chosen_1))
setorder(dat, color)
lev <- levels(as.factor(dat$n_long))
lev <- c(lev[!(lev %in% c(chosen_0, chosen_1))], chosen_0, chosen_1)
dat$n_long <- factor(dat$n_long, levels = lev)
dat$cov.1 <- factor(dat$covariate.1, 
                    labels = c("Curves for Order /s#sh/",
                               "Curves for Order /sh#s/"))
dat$dim <- factor(dat$dim, labels = c("ACO", "EPG"))
dat$alpha <- ifelse(dat$dim == 0, 0.5, 1)

# Plot the data
ggplot2::ggplot(data = dat,
                         aes(x = t, y = y_vec, group = factor(n_long), 
                             colour = color, alpha = alpha)) +
  geom_line(aes(size = color))+
  facet_grid(dim ~ cov.1) +
  scale_color_manual(values = c("grey75",
                                "steelblue3", "dodgerblue4", "cadetblue",
                                "firebrick3", "tomato2", "lightsalmon1")) +
  scale_size_manual(values = c(0.3, 0.5,0.5,0.5,0.5,0.5,0.5)) +
  theme_bw(base_size = 11) +
  theme(legend.position = "none",
        strip.text.x = element_text(size = 12)) +
  ylab("Index Values (Y)") +
  xlab("Normalized Time (t)") + 
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))
```


## Fitting the multiFAMM-Models

We fit three multiFAMM-models: `m_mul` corresponds to the model presented in the main part and `m_wei` corresponds to the model of the sensitivity analysis in the appendix using a weighted scalar product. Model `m_uni` corresponds to the model with an MFPC-cutoff based on the univariate variance. Additionally, we fit two univariate FAMM-models: `m_aco` and `m_epg`.

```{r}
# Multivariate Models
m_mul <- multiFAMM(data = phonetic, fRI_B = TRUE, fRI_C = TRUE, bs = "ps",
                   bf_mean = 8, bf_covariates = 8, m_mean = c(2, 3),
                   covariate = TRUE, num_covariates = 4,
                   covariate_form = c("by", "by", "by", "by"),
                   interaction = TRUE,
                   which_interaction = matrix(c(FALSE, TRUE, TRUE, TRUE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE),
                                              nrow = 4),
                   bf_covs = c(5, 5, 5),
                   m_covs = list(c(2, 3), c(2, 3), c(2, 3)), var_level = 1,
                   use_famm = FALSE, save_model_famm = FALSE, one_dim = NULL,
                   mfpc_cutoff = 0.95, number_mfpc = NULL,
                   mfpc_cut_method = "total_var", final_method = "w_bam",
                   mfpc_weight = FALSE)
c_mul <- multifamm:::extract_components(m_mul, dim = c("aco", "epg"))

m_wei <- multiFAMM(data = phonetic, fRI_B = TRUE, fRI_C = TRUE, bs = "ps",
                   bf_mean = 8, bf_covariates = 8, m_mean = c(2,3),
                   covariate = TRUE, num_covariates = 4,
                   covariate_form = c("by", "by", "by", "by"),
                   interaction = TRUE,
                   which_interaction = matrix(c(FALSE, TRUE, TRUE, TRUE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE),
                                              nrow = 4),
                   bf_covs = c(5, 5, 5),
                   m_covs = list(c(2, 3), c(2, 3), c(2, 3)), var_level = 1,
                   use_famm = FALSE, save_model_famm = FALSE, one_dim = NULL,
                   mfpc_cutoff = 0.95, number_mfpc = NULL,
                   mfpc_cut_method = "total_var", final_method = "w_bam",
                   mfpc_weight = TRUE)
c_wei <- multifamm:::extract_components(m_wei, dim = c("aco", "epg"))

m_uni <- multiFAMM(data = phonetic, fRI_B = TRUE, fRI_C = TRUE, bs = "ps",
                   bf_mean = 8, bf_covariates = 8, m_mean = c(2, 3),
                   covariate = TRUE, num_covariates = 4,
                   covariate_form = c("by", "by", "by", "by"),
                   interaction = TRUE,
                   which_interaction = matrix(c(FALSE, TRUE, TRUE, TRUE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE),
                                              nrow = 4),
                   bf_covs = c(5, 5, 5),
                   m_covs = list(c(2, 3), c(2, 3), c(2, 3)), var_level = 1,
                   use_famm = FALSE, save_model_famm = FALSE, one_dim = NULL,
                   mfpc_cutoff = 0.95, number_mfpc = NULL,
                   mfpc_cut_method = "unidim", final_method = "w_bam",
                   mfpc_weight = FALSE)
c_uni <- multifamm:::extract_components(m_uni, dim = c("aco", "epg"))


# Univariate Models
m_aco <- multiFAMM(data = phonetic, fRI_B = TRUE, fRI_C = TRUE, bs = "ps",
                   bf_mean = 8, bf_covariates = 8, m_mean = c(2, 3),
                   covariate = TRUE, num_covariates = 4,
                   covariate_form = c("by", "by", "by", "by"),
                   interaction = TRUE,
                   which_interaction = matrix(c(FALSE, TRUE, TRUE, TRUE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE),
                                              nrow = 4),
                   bf_covs = c(5, 5, 5),
                   m_covs = list(c(2, 3), c(2, 3), c(2, 3)), var_level = 0.95,
                   use_famm = TRUE, save_model_famm = TRUE, one_dim = "aco",
                   mfpc_cutoff = 0.95, number_mfpc = NULL,
                   mfpc_cut_method = "total_var", final_method = "w_bam",
                   mfpc_weight = FALSE)

m_epg <- multiFAMM(data = phonetic, fRI_B = TRUE, fRI_C = TRUE, bs = "ps",
                   bf_mean = 8, bf_covariates = 8, m_mean = c(2, 3),
                   covariate = TRUE, num_covariates = 4,
                   covariate_form = c("by", "by", "by", "by"),
                   interaction = TRUE,
                   which_interaction = matrix(c(FALSE, TRUE, TRUE, TRUE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE,
                                                TRUE,FALSE,FALSE,FALSE),
                                              nrow = 4),
                   bf_covs = c(5, 5, 5),
                   m_covs = list(c(2, 3), c(2, 3), c(2, 3)), var_level = 0.95,
                   use_famm = TRUE, save_model_famm = TRUE, one_dim = "epg",
                   mfpc_cutoff = 0.95, number_mfpc = NULL,
                   mfpc_cut_method = "total_var", final_method = "w_bam",
                   mfpc_weight = FALSE)
```

## Evaluation of Consonant Assimilation Data

This code reproduces the plots of the appendix for the main model.

```{r}
# Table of eigenvalue decomposition ---------------------------------------

# Calculate the untruncated MFPCA
mfpca_info <- multifamm:::prepare_mfpca(model_list = m_mul$model_indep,
                                        fRI_B = TRUE, mfpc_weight = FALSE)
MFPC <- multifamm:::conduct_mfpca(mfpca_info, mfpc_weight = FALSE)

# Extract eigenvalues
eigenvals <- unlist(lapply(seq_along(MFPC), function (x) {
  out <- MFPC[[x]]$values
  names(out) <- paste0(names(MFPC)[x], 1:length(out))
  out <- out[out>0]
  out
}))
eigenvals <- eigenvals[order(names(eigenvals))]

# Compute the univariate norms for weighting
weights_aco <- unlist(sapply(seq_along(MFPC), function(comps){
  out <- funData::norm(MFPC[[comps]]$functions$aco)
  names(out) <- paste0(names(MFPC)[comps],
                       seq_len(nObs(MFPC[[comps]]$functions)))
  out <- na.omit(out)
  out
}))
weights_aco <- weights_aco[order(names(weights_aco))]

weights_epg <- unlist(sapply(seq_along(MFPC), function(comps){
  out <- funData::norm(MFPC[[comps]]$functions$epg)
  names(out) <- paste0(names(MFPC)[comps],
                       seq_len(nObs(MFPC[[comps]]$functions)))
  out <- na.omit(out)
  out
}))
weights_epg <- weights_epg[order(names(weights_epg))]

# Extract error variance
error_var <- c_mul$error_var$uni_vars

# Compute different total variances
tot_var_mul <- sum(eigenvals, error_var)
tot_var_aco <- c(eigenvals %*% weights_aco + error_var[1])
tot_var_epg <- c(eigenvals %*% weights_epg + error_var[2])

# Which components are in the model
comps_in_m <- names(eigenvals) %in% unlist(
  lapply(seq_along(c_mul$eigenvals), function(comp){
    paste0(names(c_mul$eigenvals)[comp], 
           seq_len(length(c_mul$eigenvals[[comp]])))
}))

# Create matrix for the table
decomp <- matrix(
  c(eigenvals[comps_in_m], error_var, tot_var_mul,
    weights_aco[comps_in_m], NA, NA, NA,
    weights_epg[comps_in_m], NA, NA, NA,
    c((eigenvals*weights_aco)[comps_in_m], error_var[1])/tot_var_aco, NA, NA,
    c((eigenvals*weights_epg)[comps_in_m], NA, error_var[2])/tot_var_epg, NA,
    c(eigenvals[comps_in_m], error_var)/tot_var_mul, NA),
  nrow = 6, byrow = TRUE)
decomp[4:6, 11] <- rowSums(decomp[4:6,], na.rm = TRUE)

# Combine both to a dataframe each
vars <- c(eigenvals[comps_in_m], error_var)

# Calculate and append proportion of variance explained
props <- vars / tot_var_mul*100


# Plot the FPCs ------------------------------------------------------------

# Subject Component and rename the levels to that it is in the same line as
# the snooker plots
dat_B <- fpc_plot_helper(mcomp = c_mul, component = "B", 
                         dimlabels = c("ACO", "EPG"), two_d = FALSE, m_fac = 2)
levels(dat_B$effect) <- gsub("([0-9]+)]\\^B", "B\\1]", levels(dat_B$effect))
levels(dat_B$effect) <- paste0(levels(dat_B$effect), ":~ ",
                              round(props[grep("B", names(props))], 1), 
                              "*'% Variation'")

# Plot the data
ggplot2::ggplot(data = dat_B, aes(x = t)) +
  geom_line(aes(y = val), size = 0.2) +
  geom_text(aes(y = val_p), label = "+", size = 1.5, col = "firebrick3") +
  geom_text(aes(y = val_m), label = "-", size = 1.5, col = "dodgerblue4") +
  geom_hline(yintercept = 0, linetype = "dotted", size = 0.2) +
  facet_grid(dim ~ effect, labeller = label_parsed) +
  xlab("Normalized Time (t)") +
  ylab(expression("MFPC for Speaker (" ~ psi[B]^ ~ "(d)" ~ "(t) )")) +
  theme_bw(base_size = 8) +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

# Subject Component and rename the levels to that it is in the same line as
# the snooker plots
dat_E <- fpc_plot_helper(mcomp = c_mul, component = "E", 
                         dimlabels = c("ACO", "EPG"), two_d = FALSE, m_fac = 2)
levels(dat_E$effect) <- gsub("([0-9]+)]\\^E", "E\\1]", levels(dat_E$effect))
levels(dat_E$effect) <- paste0(levels(dat_E$effect), ":~ ",
                               round(props[grep("E", names(props))], 1), 
                               "*'% Variation'")

# Plot the data
ggplot2::ggplot(data = dat_E, aes(x = t)) +
  geom_line(aes(y = val), size = 0.2) +
  geom_text(aes(y = val_p), label = "+", size = 1.5, col = "firebrick3") +
  geom_text(aes(y = val_m), label = "-", size = 1.5, col = "dodgerblue4") +
  geom_hline(yintercept = 0, linetype = "dotted", size = 0.2) +
  facet_grid(dim ~ effect, labeller = label_parsed) +
  xlab("Normalized Time (t)") +
  ylab(expression("MFPC for Curve (" ~ psi[E]^ ~ "(d)" ~ "(t) )")) +
  theme_bw(base_size = 8) +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

# Plot the covariance surface of B
cov_B <- covariance_surf_plot_helper(c_mul, "B", dimlabels = c("ACO", "EPG"))
ggplot2::ggplot(data = cov_B, aes(x = col, y = row, z = value)) +
  stat_contour(geom = "polygon", aes(fill = ..level..), na.rm = TRUE) +
  geom_tile(aes(fill = value)) +
  stat_contour(bins = 10, col = "black", na.rm = TRUE, size = 0.2) +
  facet_grid(col_dim ~ row_dim) +
  scale_fill_viridis(option = "D") +
  labs(title = "Covariance for B",
       x = NULL, y = NULL) +
  theme_bw(base_size = 8) +
  theme(plot.title = element_text(hjust = 0.5), 
        legend.title = element_blank(),
        legend.position = "bottom",
        aspect.ratio = 1,
        panel.spacing = unit(0.4, "lines")) +
  scale_x_continuous(expand = c(0,0), 
                     breaks = c(0, 0.25, 0.5, 0.75, 1),
                     labels=c("0", "0.25", "0.5", "0.75", "1")) +
  scale_y_continuous(expand = c(0,0), 
                     breaks = c(0, 0.25, 0.5, 0.75, 1),
                     labels=c("0", "0.25", "0.5", "0.75", "1")) +
  guides(fill = guide_colorbar(barheight = 0.3))

# Plot the covariance surface of E
cov_E <- multifamm:::covariance_surf_plot_helper(c_mul, "E", 
                                                 dimlabels = c("ACO", "EPG"))
ggplot2::ggplot(data = cov_E, aes(x = col, y = row, z = value)) +
  stat_contour(geom = "polygon", aes(fill = ..level..), na.rm = TRUE) +
  geom_tile(aes(fill = value)) +
  stat_contour(bins = 10, col = "black", na.rm = TRUE, size = 0.2) +
  facet_grid(col_dim ~ row_dim) +
  scale_fill_viridis(option = "D") +
  labs(title = "Covariance Component E",
       x = NULL, y = NULL) +
  theme_bw(base_size = 8) +
  theme(plot.title = element_text(hjust = 0.5), 
        legend.title = element_blank(),
        legend.position = "bottom",
        aspect.ratio = 1,
        panel.spacing = unit(0.4, "lines")) +
  scale_x_continuous(expand = c(0,0), 
                     breaks = c(0, 0.25, 0.5, 0.75, 1),
                     labels=c("0", "0.25", "0.5", "0.75", "1")) +
  scale_y_continuous(expand = c(0,0), 
                     breaks = c(0, 0.25, 0.5, 0.75, 1),
                     labels=c("0", "0.25", "0.5", "0.75", "1")) +
  guides(fill = guide_colorbar(barheight = 0.3))


# Plot the covariate effects ----------------------------------------------

# Set up
aco_pr <- multifamm:::predict_sparseFLMM_covar(m_aco)
dat_n <- covariate_plot_helper(mcomp = c_mul, dimlabels = c("ACO", "EPG"))

dat <- covariate_comp_plot_helper(dat_m = dat_n, aco_pr = aco_pr, epg_pr = NULL,
                                  mul_level = c("f[1](t)"), uni_effect <- c(4))

# Plot the covariate effects per order
dat1 <- covariate_comp_plot_helper( 
  dat_m = dat_n, aco_pr = aco_pr, epg_pr = NULL,
  mul_level = c("f[0](t)", "f[2](t)", "f[3](t)", "f[4](t)"),
  uni_effect <- c(1, 5, 6, 7))
dat2 <-covariate_comp_plot_helper(
  dat_m = dat_n, aco_pr = aco_pr, epg_pr = NULL,
  mul_level = c("f[1](t)", "f[5](t)", "f[6](t)", "f[7](t)"),
  uni_effect <- c(4, 8, 9, 10))


ggplot2::ggplot(data = dat1, aes(x = t)) +
  geom_line(aes(y = y), size = 0.25) +
  geom_line(aes(y = y_p), linetype = "dashed", size = 0.25) +
  geom_line(aes(y = y_m), linetype = "dashed", size = 0.25) +
  geom_line(aes(y = y_uni), color = "firebrick3", size = 0.25) +
  geom_line(aes(y = y_uni_p), color = "firebrick3", linetype = "dashed",
            size = 0.25) +
  geom_line(aes(y = y_uni_m), color = "firebrick3", linetype = "dashed",
            size = 0.25) +
  geom_hline(yintercept = 0, linetype = "dotted", size = 0.3) +
  geom_rect(aes(ymin = min_val, ymax = max_val, xmin = x_start, xmax = x_end,
                fill = se_dif), alpha = 0.15) +
  facet_grid(dim ~ effect, labeller = label_parsed) +
  xlab("Normalized Time (t)") +
  ylab(expression("Effect Function (" ~ f^(d)~"(t) )")) +
  theme_bw(base_size = 8)  +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("firebrick3", NA)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

ggplot2::ggplot(data = dat2, aes(x = t)) +
  geom_line(aes(y = y), size = 0.25) +
  geom_line(aes(y = y_p), linetype = "dashed", size = 0.25) +
  geom_line(aes(y = y_m), linetype = "dashed", size = 0.25) +
  geom_line(aes(y = y_uni), color = "firebrick3", size = 0.25) +
  geom_line(aes(y = y_uni_p), color = "firebrick3", linetype = "dashed",
            size = 0.25) +
  geom_line(aes(y = y_uni_m), color = "firebrick3", linetype = "dashed",
            size = 0.25) +
  geom_hline(yintercept = 0, linetype = "dotted", size = 0.3) +
  geom_rect(aes(ymin = min_val, ymax = max_val, xmin = x_start, xmax = x_end,
                fill = se_dif), alpha = 0.15) +
  facet_grid(dim ~ effect, labeller = label_parsed) +
  xlab("Normalized Time (t)") +
  ylab(expression("Effect Function (" ~ f^(d)~"(t) )")) +
  theme_bw(base_size = 8)  +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("firebrick3", NA)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))
```


## Sensitivity Analysis

The following code gives the analysis of the model using the weighted scalar product.

```{r}
# Table of eigenvalue decomposition ---------------------------------------

# Calculate the untruncated MFPCA
mfpca_info <- multifamm:::prepare_mfpca(model_list = m_wei$model_indep,
                                        fRI_B = TRUE, mfpc_weight = FALSE)
MFPC <- multifamm:::conduct_mfpca(mfpca_info, mfpc_weight = FALSE)

# Extract error variance
error_var <- c_wei$error_var$uni_vars

# Extract eigenvalues
eigenvals <- unlist(lapply(seq_along(MFPC), function (x) {
  out <- MFPC[[x]]$values
  names(out) <- paste0(names(MFPC)[x], 1:length(out))
  out <- out[out>0]
  out
}))
eigenvals <- eigenvals[order(names(eigenvals))]

# Compute the univariate norms for weighting
weights_aco <- unlist(sapply(seq_along(MFPC), function(comps){
  out <- funData::norm(MFPC[[comps]]$functions$aco) 
  names(out) <- paste0(names(MFPC)[comps],
                       seq_len(nObs(MFPC[[comps]]$functions)))
  out <- na.omit(out)
  out
}))
weights_aco <- weights_aco[order(names(weights_aco))]

weights_epg <- unlist(sapply(seq_along(MFPC), function(comps){
  out <- funData::norm(MFPC[[comps]]$functions$epg)
  names(out) <- paste0(names(MFPC)[comps],
                       seq_len(nObs(MFPC[[comps]]$functions)))
  out <- na.omit(out)
  out
}))
weights_epg <- weights_epg[order(names(weights_epg))]

# Compute different total variances
tot_var_mul <- sum(eigenvals, length(error_var))
tot_var_aco <- c(eigenvals %*% weights_aco + error_var[1])
tot_var_epg <- c(eigenvals %*% weights_epg + error_var[2])

# Which components are in the model
comps_in_m <- names(eigenvals) %in% unlist(
  lapply(seq_along(c_wei$eigenvals), function(comp){
    paste0(names(c_wei$eigenvals)[comp], 
           seq_len(length(c_wei$eigenvals[[comp]])))
  }))

# Create matrix for the table
decomp <- matrix(
  c(eigenvals[comps_in_m], error_var, tot_var_mul,
    weights_aco[comps_in_m]*1/error_var[1], NA, NA, NA,
    weights_epg[comps_in_m]*1/error_var[2], NA, NA, NA,
    c((eigenvals*weights_aco)[comps_in_m], error_var[1])/tot_var_aco, NA, NA,
    c((eigenvals*weights_epg)[comps_in_m], NA, error_var[2])/tot_var_epg, NA,
    c(eigenvals[comps_in_m], rep(1, length(error_var)))/tot_var_mul, NA),
  nrow = 6, byrow = TRUE)
decomp[4:6, 11] <- rowSums(decomp[4:6,], na.rm = TRUE)

props <- eigenvals[comps_in_m]/tot_var_mul*100


# Plot the FPCs to be included in the Paper -------------------------------

# Subject Component and rename the levels to that it is in the same line as
# the snooker plots
dat_B <- fpc_plot_helper(mcomp = c_wei, component = "B", 
                         dimlabels = c("ACO", "EPG"), two_d = FALSE,
                         m_fac = 2)
levels(dat_B$effect) <- gsub("([0-9]+)]\\^B", "B\\1]", levels(dat_B$effect))
levels(dat_B$effect) <- paste0(levels(dat_B$effect), ":~ ",
                               round(props[grep("B", names(props))], 1), 
                               "*'% Variation'")

# Plot the data
ggplot2::ggplot(data = dat_B, aes(x = t)) +
  geom_line(aes(y = val), size = 0.2) +
  geom_text(aes(y = val_p), label = "+", size = 1.5, col = "firebrick3") +
  geom_text(aes(y = val_m), label = "-", size = 1.5, col = "dodgerblue4") +
  geom_hline(yintercept = 0, linetype = "dotted", size = 0.2) +
  facet_grid(dim ~ effect, labeller = label_parsed) +
  xlab("Normalized Time (t)") +
  ylab(expression("MFPC for Speaker (" ~ psi[B]^ ~ "(d)" ~ "(t) )")) +
  theme_bw(base_size = 8) +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

# Subject Component and rename the levels to that it is in the same line as
# the snooker plots
dat_E <- fpc_plot_helper(mcomp = c_wei, component = "E", 
                         dimlabels = c("ACO", "EPG"), two_d = FALSE,
                         m_fac = 2)
levels(dat_E$effect) <- gsub("([0-9]+)]\\^E", "E\\1]", levels(dat_E$effect))
levels(dat_E$effect) <- paste0(levels(dat_E$effect), ":~ ",
                               round(props[grep("E", names(props))], 1), 
                               "*'% Variation'")

# Plot the data
ggplot2::ggplot(data = dat_E, aes(x = t)) +
  geom_line(aes(y = val), size = 0.2) +
  geom_text(aes(y = val_p), label = "+", size = 1.5, col = "firebrick3") +
  geom_text(aes(y = val_m), label = "-", size = 1.5, col = "dodgerblue4") +
  geom_hline(yintercept = 0, linetype = "dotted", size = 0.2) +
  facet_grid(dim ~ effect, labeller = label_parsed) +
  xlab("Normalized Time (t)") +
  ylab(expression("MFPC for Curve (" ~ psi[E]^ ~ "(d)" ~ "(t) )")) +
  theme_bw(base_size = 8) +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

```

The following code compares the multivariate and the univariate models using the univariate root relative MSE.

```{r}
# Gather all the data -----------------------------------------------------

dat <- data.table(
  y_vec = m_uni$data$y_vec,
  t = m_uni$data$t,
  n_long = as.integer(as.character(m_uni$data$n_long)),
  dim = m_uni$data$dim,
  r_uni = m_uni$model$residuals
)
resid_aco <- m_aco$fpc_famm_hat_tri_constr$famm_estim$residuals
resid_epg <- m_epg$fpc_famm_hat_tri_constr$famm_estim$residuals
dat <- cbind(dat, r_ane = c(resid_aco, resid_epg))


# Fundata for Fit and Observations ----------------------------------------

# MultiFunData for Fit and Y values
y_val <- lapply(split(dat, dat$dim), function(x) {
  uhu <- split(x, x$n_long)
  irregFunData(argvals = lapply(uhu, "[[", "t"),
               X = lapply(uhu, "[[", "y_vec"))
})
y_fit_uni <- lapply(split(dat, dat$dim), function(x) {
  uhu <- split(x, x$n_long)
  irregFunData(argvals = lapply(uhu, "[[", "t"),
               X = lapply(uhu, "[[", "r_uni"))
})
y_fit_ane <- lapply(split(dat, dat$dim), function(x) {
  uhu <- split(x, x$n_long)
  irregFunData(argvals = lapply(uhu, "[[", "t"),
               X = lapply(uhu, "[[", "r_ane"))
})



# UMSE Values -------------------------------------------------------------

umse_uni <- urrMSE(fun_true = y_val, fun_estim = y_fit_uni, flip = FALSE, 
                   relative = TRUE)
umse_ane <- urrMSE(fun_true = y_val, fun_estim = y_fit_ane, flip = FALSE, 
                   relative = TRUE)
```


