---
title: "snooker_training_data"
author: Alexander Volkmann
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Snooker Training Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(data.table)
library(funData)
library(grid)
library(gridExtra)
library(multifamm)
library(multifammPaper)
library(sparseFLMM)
library(tidyverse)
library(viridis)
data("snooker")
```

# Analysis of the Snooker Training Data

This vignette provides the code to reproduce the analysis of the snooker training data presented in the paper "Multivariate functional additive mixed models" (Volkmann et al., 2021). Note that this vignette does not execute the presented code because the required computing resources can be large.

## Plot the Data

```{r}
# Multivariate Observation Plot -------------------------------------------

# Choose random individuals
set.seed(123)
chosen_0 <- sample(unique(subset(snooker, covariate.1 == 0)$n_long), size = 3)
chosen_1 <- sample(unique(subset(snooker, covariate.1 == 1)$n_long), size = 3)

# Prepare data for plotting
snooker$color <- factor(snooker$n_long*(snooker$n_long %in% 
                                          c(chosen_0, chosen_1)),
                    levels = c(0, chosen_0, chosen_1))
helpdat <- data.frame(
  do.call(rbind, strsplit(as.character(snooker$dim), ".", fixed = TRUE)))
names(helpdat) <- c("location", "axis")
snooker <- cbind(snooker, helpdat)
snooker <- snooker %>%
  unite(curve_group, n_long, location) %>%
  select(-dim) %>%
  spread(axis, y_vec)
lev <- levels(as.factor(snooker$curve_group))
combined_lev <- grepl(paste(c(chosen_0, chosen_1), collapse = "|"), lev)
lev <- c(lev[!combined_lev], lev[combined_lev])
snooker$curve_group <- factor(snooker$curve_group, levels = lev)
snooker$cov.1 <- factor(snooker$covariate.1, 
                    labels = c("Shots of Unskilled Players",
                               "Shots of Skilled Players"))

# Create data with starts of trajectories
beg <- snooker %>%
  group_by(curve_group) %>%
  filter(color != "0") %>%
  slice(which.min(t)) %>%
  ungroup()

ggplot2::ggplot() +
  geom_path(data = snooker, aes(x = x, y = y, group = curve_group, 
                                colour = color, size = color), alpha = 0.5) +
  facet_grid(cols = vars(cov.1)) +
  scale_color_manual(values = c("grey75",
                                "steelblue3", "dodgerblue4", "cadetblue",
                                "firebrick3", "tomato2", "lightsalmon1")) +
  scale_size_manual(values =  c(0.3, 0.5,0.5,0.5,0.5,0.5,0.5)) +
  theme_bw(base_size = 12) +
  theme(legend.position = "none",
        strip.text.x = element_text(size = 14)) +
  ylab("Y") +
  xlab("X") +
  geom_point(data = beg, aes(x = x, y = y),
             shape = 8, size = 0.8, colour = "black", alpha = 0.5)


# Univariate Observation Plot ---------------------------------------------

snooker$location <- as.factor(sapply(strsplit(as.character(snooker$dim),
                                              split = "\\."), "[[", 1))
snooker$axis <- as.factor(sapply(strsplit(as.character(snooker$dim),
                                          split = "\\."), "[[", 2))
snooker$cov.1 <- factor(snooker$covariate.1, 
                        labels = c("Shots of Unskilled Players",
                                   "Shots of Skilled Players"))
ggplot2::ggplot(data = snooker,
                aes(x = t, y = y_vec, group = n_long)) + 
  geom_line(alpha = 0.1) +
  facet_wrap(axis ~ location, scales = "free") +
  scale_size_manual(values =  0.3) + 
  theme_bw(base_size = 8) +
  theme(legend.position = "none") +
  xlab("Standardized Time (t)") +
  ylab("Value") + 
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))
```


## Fitting the multiFAMM-Models

We fit two multiFAMM-models: `m` corresponds to the model presented in the main part and `m_sens` corresponds to the model of the sensitivity analysis in the appendix.
```{r}
m <- multiFAMM(data = snooker, 
               fRI_B = TRUE, fRI_C = TRUE, nested = TRUE,
               bs = "ps", bf_mean = 8, bf_covariates = 8, m_mean = c(2, 1), 
               covariate = TRUE, num_covariates = 4, 
               covariate_form = rep("by", times = 4),
               interaction = FALSE, 
               bf_covs = c(5, 5, 5),
               m_covs = list(c(2, 1), c(2, 1), c(2, 1)), var_level = 1,
               use_famm = FALSE, save_model_famm = FALSE, one_dim = NULL, 
               mfpc_weight = FALSE, mfpc_cutoff = 0.95, number_mfpc = NULL, 
               mfpc_cut_method = "total_var", final_method = "bam")

m_sens <- multiFAMM(data = snooker, 
                    fRI_B = TRUE, fRI_C = TRUE, nested = TRUE,
                    bs = "ps", bf_mean = 8, bf_covariates = 8, m_mean = c(2, 1), 
                    covariate = TRUE, num_covariates = 4, 
                    covariate_form = rep("by", times = 4),
                    interaction = FALSE, 
                    bf_covs = c(5, 5, 5),
                    m_covs = list(c(2, 1), c(2, 1), c(2, 1)), var_level = 1,
                    use_famm = FALSE, save_model_famm = FALSE, one_dim = NULL, 
                    mfpc_weight = FALSE, mfpc_cutoff = 0.99, number_mfpc = NULL, 
                    mfpc_cut_method = "total_var", final_method = "w_bam")
```

## Evaluation of Snooker Data

This code reproduces the plots of the main part and the appendix.
```{r}
# Set up ------------------------------------------------------------------
dimlabels <- names(m$model_indep)
dat_n <- covariate_plot_helper(model = m2, dimlabels = dimlabels)


# Table of eigenvalue decomposition ---------------------------------------

# Extract eigenvalues
eigenvals <- lapply(seq_along(m$mfpc), function (x) {
  out <- m$mfpc[[x]]$values
  names(out) <- paste0(names(m$mfpc)[x], 1:length(out))
  out
})

# Extract error variance
error_var <- lapply(seq_along(m$model_indep), function (x) {
  out <- m$model_indep[[x]]$cov_hat_tri_constr$sigmasq
  names(out) <- paste0("Sigma2", names(m$model_indep)[[x]])
  out
})

# Calculate proportion of variance explained
mfpca_info <- multifamm:::prepare_mfpca(model_list = m2$model_indep,
                                        fRI_B = TRUE, mfpc_weight = FALSE)
MFPC <- multifamm:::conduct_mfpca(mfpca_info, mfpc_weight = FALSE)
tot_var <- sum(unlist(lapply(MFPC, "[[", "values")), unlist(error_var))
props <- vars/tot_var*100


# Plot all the different FPCs ---------------------------------------------

# Loop over all possible plots
for (u in c("B", "C", "E")) {
  dat <- fpc_plot_helper(model = m, component = u, dimlabels = dimlabels,
                         two_d = TRUE, m_fac = 2)
  beg <- dat %>%
    group_by(effect) %>%
    filter(t == min(t))
  
  for (i in levels(dat$effect)) {
    j <- which(levels(dat$effect) == i)
    perc_exp <- round(props[paste0(u, j)], 1)
    p <- ggplot2::ggplot(data = dat %>% filter(effect == i),
                         aes(group = location)) +
      geom_path(aes(x = x_val, y = y_val), size = 0.5) +
      geom_text(aes(x = x_val_p, y = y_val_p), label = "+", size = 2,
                col = "firebrick3") +
      geom_text(aes(x = x_val_m, y = y_val_m), label = "-", size = 2,
                col = "dodgerblue4") +
      geom_point(data = beg %>% filter(effect == i),
                 aes(x = x_val, y = y_val),
                 shape = 8, size = 0.8, colour = "black", alpha = 0.5) +
      geom_point(data = beg %>% filter(effect == i),
                 aes(x = x_val_m, y = y_val_m),
                 shape = 8, size = 0.8, colour = "dodgerblue4", alpha = 0.5) +
      geom_point(data = beg %>% filter(effect == i),
                 aes(x = x_val_p, y = y_val_p),
                 shape = 8, size = 0.8, colour = "firebrick3", alpha = 0.5) +
      
      xlab("X") +
      ylab("Y") +
      ggtitle(bquote(psi[.(u)*.(j)](t):~.(perc_exp)*"% Variation")) +
      theme_bw(base_size = 8)
    assign(paste0("p_", u, "_", j), p)
  }
}


# Plots for all fixed covariate effects -----------------------------------

# All the combinations without the intercept
plot_covs <- list(c(0, 1), c(0, 2), c(0, 3), c(0, 2, 3, 4))

for (i in plot_covs) {
  dat_s <- covariate_plot_helper_2d_transform(data = dat_n, covs = i)
  beg_s <- dat_s %>%
    group_by(dim) %>%
    filter(t == min(t))
  
  # Plot the trajectory data
  p1 <- ggplot2::ggplot(data = dat_s) +
    geom_path(aes(x = val_x, y = val_y, group = dim), size = 0.5, 
              col = "dodgerblue4") +
    geom_path(aes(x = val_x_int, y = val_y_int, group = dim),
              col = "firebrick3", size = 0.5) +
    geom_point(data = beg_s,
               aes(x = val_x, y = val_y),
               shape = 8, size = 0.8, colour = "dodgerblue4", alpha = 0.5) +
    geom_point(data = beg_s,
               aes(x = val_x_int, y = val_y_int),
               shape = 8, size = 0.8, colour = "firebrick3", alpha = 0.5) +
    xlab("X") +
    ylab("Y") +
    theme_bw(base_size = 8) 
  
  # Plot the vertical univariate effects
  p2 <- ggplot2::ggplot(data = dat_n %>% 
                          filter(dim %in% c("elbow.y", "hand.y", "shoulder.y"),
                                 cov == i[length(i)]),
                        aes(x = t)) +
    geom_line(aes(y = y), size = 0.25) +
    geom_line(aes(y = y_p), linetype = "dotted", size = 0.25) +
    geom_line(aes(y = y_m), linetype = "dotted", size = 0.25) +
    geom_hline(yintercept = 0, size = 0.2, linetype = "longdash",
               col = "dodgerblue4") +
    facet_grid(rows = vars(dim), scales = "free") +
    xlab("Standardized Time (t)") +
    ylab(NULL) +
    theme_grey(base_size = 8) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(fill = NA),
          panel.background = element_rect(fill = NA),
          text = element_text(size = 5),
          strip.text.y = element_text(size = 7)) +
    scale_x_continuous(breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1"))
  
  # Plot the horizontal univariate effects
  p3 <- ggplot2::ggplot(data = dat_n %>% 
                          filter(dim %in% c("elbow.x", "hand.x", "shoulder.x"), 
                                 cov == i[length(i)]),
                        aes(x = t)) +
    geom_line(aes(y = y), size = 0.25) +
    geom_line(aes(y = y_p), linetype = "dotted", size = 0.25) +
    geom_line(aes(y = y_m), linetype = "dotted", size = 0.25) +
    geom_hline(yintercept = 0, size = 0.2, linetype = "longdash",
               col = "dodgerblue4") +
    facet_grid(cols = vars(dim), scales = "free") +
    xlab("Standardized Time (t)") +
    ylab(NULL) +
    theme_grey(base_size = 8) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(fill = NA),
          panel.background = element_rect(fill = NA),
          text = element_text(size = 5),
          strip.text.x = element_text(size = 7)) +
    scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

  # Combine the plots
  if(length(i) == 4) {
    title <- "f[0]+f[2]+f[3]~(+f[4])"
  } else {
    title <- paste0("f[0]~(+f[", i[length(i)], "])")
  }
  
  g <- grid.arrange(p1, p2, p3, layout_matrix = rbind(c(1, 1, 1, 2),
                                                      c(1, 1, 1, 2),
                                                      c(1, 1, 1, 2), 
                                                      c(3, 3, 3, 4)),
                    top = grid.text(parse(text = title)))
  assign(paste("g", paste(i, collapse = "_"), sep = "_"), g)
  
}


# Plot the intercept ------------------------------------------------------

dat_s <- covariate_plot_helper_2d_transform(data = dat_n, covs = 0)
beg_s <- dat_s %>%
  group_by(dim) %>%
  filter(t == min(t))

# Plot the data
p1 <- ggplot2::ggplot(data = dat_s) +
  geom_path(aes(x = val_x, y = val_y, group = dim), size = 0.5, 
            col = "dodgerblue4") +
  geom_point(data = beg_s,
             aes(x = val_x, y = val_y),
             shape = 8, size = 0.8, colour = "dodgerblue4", alpha = 0.5) +
  xlab("X") +
  ylab("Y") +
  theme_bw(base_size = 8) 

p2 <- ggplot2::ggplot(data = dat_n %>% 
                        filter(dim %in% c("elbow.y", "hand.y", "shoulder.y"),
                               cov == 0),
                      aes(x = t)) +
  geom_line(aes(y = y), size = 0.25) +
  geom_line(aes(y = y_p), linetype = "dotted", size = 0.25) +
  geom_line(aes(y = y_m), linetype = "dotted", size = 0.25) +
  geom_hline(yintercept = 0, size = 0.2, linetype = "longdash",
             col = "grey60") +
  facet_grid(rows = vars(dim), scales = "free") +
  xlab("Standardized Time (t)") +
  ylab(NULL) +
  theme_grey(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA),
        panel.background = element_rect(fill = NA),
        text = element_text(size = 5),
        strip.text.y = element_text(size = 7)) +
  scale_x_continuous(breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1"))

p3 <- ggplot2::ggplot(data = dat_n %>% 
                        filter(dim %in% c("elbow.x", "hand.x", "shoulder.x"), 
                               cov == 0),
                      aes(x = t)) +
  geom_line(aes(y = y), size = 0.25) +
  geom_line(aes(y = y_p), linetype = "dotted", size = 0.25) +
  geom_line(aes(y = y_m), linetype = "dotted", size = 0.25) +
  geom_hline(yintercept = 0, size = 0.2, linetype = "longdash",
             col = "grey60") +
  facet_grid(cols = vars(dim), scales = "free") +
  xlab("Standardized Time (t)") +
  ylab(NULL) +
  theme_grey(base_size = 8) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA),
        panel.background = element_rect(fill = NA),
        text = element_text(size = 5),
        strip.text.x = element_text(size = 7)) +
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))

g <- grid.arrange(p1, p2, p3, layout_matrix = rbind(c(1, 1, 1, 2),
                                               c(1, 1, 1, 2),
                                               c(1, 1, 1, 2), 
                                               c(3, 3, 3, 4)),
                  top = grid.text(expression(f[0])))

```


## Sensitivity Analysis

```{r}
# Model Fit ---------------------------------------------------------------

# MultiFunData for Fit and Y values
# For main model
y_val <- lapply(split(m$data, m$data$dim), function(x) {
  uhu <- split(x, x$n_long)
  irregFunData(argvals = lapply(uhu, "[[", "t"),
                          X = lapply(uhu, "[[", "y_vec"))
})
y_fit <- lapply(split(cbind(m$data, fit = m$model$fitted.values),
                                   m$data$dim), function(x) {
  uhu <- split(x, x$n_long)
  irregFunData(argvals = lapply(uhu, "[[", "t"),
                          X = lapply(uhu, "[[", "fit"))
})
rel <- urrMSE(fun_true = y_val, fun_estim = y_fit, flip = FALSE, 
              relative = TRUE)


# Calculate the mrrMSE Contributions --------------------------------------

# Transform the list of irregFunDatas to a list of multiFunDatas per observation
dif <- mapply(function (val, fit) val - fit, val = y_val, fit = y_fit,
              SIMPLIFY = FALSE)
mul_norm <- unlist(lapply(seq_len(nObs(dif[[1]])), function (obs) {
  do.call(sum, lapply(dif, function (dim) {
    norm(extractObs(dim, obs), squared = TRUE, fullDom = TRUE)
  }))
}))
names(mul_norm) <- names(y_val$elbow.x)

# Extract the quantiles according to the mrrMSE
sel <- sapply(quantile(mul_norm, probs = c(0, 0.25, 0.5, 0.75, 1), 
                       type = 3), 
              function(x) {names(which(mul_norm == x))})
names(sel)[c(1, length(sel))] <- c("Min", "Max")


# Plot Observations vs Fitted Trajectories --------------------------------

pl <- plot_snooker_fit(obs = sel, model = m, model_comp = m_sens)


# Contribution of Fixed Effects -------------------------------------------

mat <- predict(m$model, type = "terms")
pred_var <- do.call(rbind, lapply(levels(m$data$dim), function (dim) {
  dat <- split(as.data.frame(mat), m$data$dim)[[dim]]
  vars <- sapply(dat, var)
  vars <- vars[vars > 0]
  rat <- vars / sum(vars)
}))


# Residual Analysis -------------------------------------------------------

dat <- cbind(m$data, resid = m$model$residuals, 
             resid4 = m_sens$model$residuals) %>%
  mutate(location = as.factor(sapply(strsplit(as.character(snooker$dim), 
                                              split = "\\."), "[[", 1)),
         axis = as.factor(sapply(strsplit(as.character(snooker$dim),
                                           split = "\\."), "[[", 2)))
p1 <- ggplot(data = dat, aes(x = t, y = resid)) +
  geom_point(alpha = 0.2, size = 0.5) +
  facet_wrap(axis ~ location) +
  xlab("Standardized Time (t)") + 
  theme_bw(base_size = 8) +
  ylab("Residuals") + 
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1"))+
  ggtitle("Residuals of Model Fit")
p2 <- ggplot(data = dat, aes(x = t, y = resid4)) +
  geom_point(alpha = 0.2, size = 0.5) +
  facet_wrap(axis ~ location) +
  xlab("Standardized Time (t)") + 
  theme_bw(base_size = 8) +
  ylab("Residuals") + 
  scale_x_continuous(labels = c("0", "0.25", "0.5", "0.75", "1")) +
  ylim(range(dat$resid))+
  ggtitle("Residuals of Sensitivity Analysis")


# Check for Autocorrelation -----------------------------------------------
# Create data for covariance estimation
dat_y <- data.table(
  y_vec = m$data$y_vec,
  t = m$data$t,
  n_long = as.integer(as.character(m$data$n_long)),
  subject_long = as.integer(as.character(m$data$subject_long)),
  dim = m$data$dim
)
dat_r <- data.table(
  y_vec = m$model$residuals,
  t = m$data$t,
  n_long = as.integer(as.character(m$data$n_long)),
  subject_long = as.integer(as.character(m$data$subject_long)),
  dim = m$data$dim
)
dat_r4 <- data.table(
  y_vec = m_sens$model$residuals,
  t = m_sens$data$t,
  n_long = as.integer(as.character(m_sens$data$n_long)),
  subject_long = as.integer(as.character(m_sens$data$subject_long)),
  dim = m_sens$data$dim
)

# Covariance estimation
cov_y <- estim_overall_cov(data = dat_y)
cov_r <- estim_overall_cov(data = dat_r)
cov_r4 <- estim_overall_cov(data = dat_r4)

# Focus on the locations of interest
cov_y_el <- list(eigenfcts = list(E = multiFunData(cov_y$E$functions$elbow.x,
                                                    cov_y$E$functions$elbow.y)),
                 eigenvals = list(E = cov_y$E$values))
cov_y_ha <- list(eigenfcts = list(E = multiFunData(cov_y$E$functions$hand.x,
                                                    cov_y$E$functions$hand.y)),
                 eigenvals = list(E = cov_y$E$values))
cov_y_sh <- list(eigenfcts = list(E = multiFunData(cov_y$E$functions$shoulder.x,
                                                 cov_y$E$functions$shoulder.y)),
                 eigenvals = list(E = cov_y$E$values))
cov_r_el <- list(eigenfcts = list(E = multiFunData(cov_r$E$functions$elbow.x,
                                                   cov_r$E$functions$elbow.y)),
                 eigenvals = list(E = cov_r$E$values))
cov_r_ha <- list(eigenfcts = list(E = multiFunData(cov_r$E$functions$hand.x,
                                                   cov_r$E$functions$hand.y)),
                 eigenvals = list(E = cov_r$E$values))
cov_r_sh <- list(eigenfcts = list(E = multiFunData(cov_r$E$functions$shoulder.x,
                                                 cov_r$E$functions$shoulder.y)),
                 eigenvals = list(E = cov_r$E$values))
cov_r4_el <- list(eigenfcts = list(E = multiFunData(cov_r4$E$functions$elbow.x,
                                                  cov_r4$E$functions$elbow.y)),
                 eigenvals = list(E = cov_r4$E$values))
cov_r4_ha <- list(eigenfcts = list(E = multiFunData(cov_r4$E$functions$hand.x,
                                                   cov_r4$E$functions$hand.y)),
                 eigenvals = list(E = cov_r4$E$values))
cov_r4_sh <- list(eigenfcts = list(
                              E = multiFunData(cov_r4$E$functions$shoulder.x,
                                               cov_r4$E$functions$shoulder.y)),
                 eigenvals = list(E = cov_r4$E$values))

# Data of the correlation surfaces
cov_y_surf_el <- covariance_surf_plot_helper(cov_y_el, "E", corr = TRUE, 
                                             dimlabels = c("elbow.x", 
                                                           "elbow.y"))
cov_y_surf_ha <- covariance_surf_plot_helper(cov_y_ha, "E", corr = TRUE, 
                                             dimlabels = c("hand.x", "hand.y"))
cov_y_surf_sh <- covariance_surf_plot_helper(cov_y_sh, "E", corr = TRUE,
                                             dimlabels = c("shoulder.x", 
                                                           "shoulder.y"))
cov_r_surf_el <- covariance_surf_plot_helper(cov_r_el, "E", corr = TRUE, 
                                             dimlabels = c("elbow.x", 
                                                           "elbow.y"))
cov_r_surf_ha <- covariance_surf_plot_helper(cov_r_ha, "E", corr = TRUE, 
                                             dimlabels = c("hand.x", "hand.y"))
cov_r_surf_sh <- covariance_surf_plot_helper(cov_r_sh, "E", corr = TRUE,
                                             dimlabels = c("shoulder.x", 
                                                           "shoulder.y"))
cov_r4_surf_el <- covariance_surf_plot_helper(cov_r4_el, "E", corr = TRUE, 
                                              dimlabels = c("elbow.x", 
                                                            "elbow.y"))
cov_r4_surf_ha <- covariance_surf_plot_helper(cov_r4_ha, "E", corr = TRUE, 
                                              dimlabels = c("hand.x", "hand.y"))
cov_r4_surf_sh <- covariance_surf_plot_helper(cov_r4_sh, "E", corr = TRUE,
                                              dimlabels = c("shoulder.x", 
                                                            "shoulder.y"))

# Approximate the autocorrelation function
dat_y <- rbind(approx_autocor(cov_y_surf_el), approx_autocor(cov_y_surf_ha),
               approx_autocor(cov_y_surf_sh)) %>%
  mutate(source = factor("Y"))
dat_r <- rbind(approx_autocor(cov_r_surf_el), approx_autocor(cov_r_surf_ha),
               approx_autocor(cov_r_surf_sh)) %>%
  mutate(source = factor("r (m2)"))
dat_r4 <- rbind(approx_autocor(cov_r4_surf_el), approx_autocor(cov_r4_surf_ha),
               approx_autocor(cov_r4_surf_sh)) %>%
  mutate(source = factor("r (m4)"))
dat <- rbind(dat_y, dat_r, dat_r4) %>%
  mutate(location = as.factor(sapply(strsplit(as.character(dim), 
                                              split = "\\."), "[[", 1)),
              axis = as.factor(sapply(strsplit(as.character(dim),
                                               split = "\\."), "[[", 2)))
ggplot(dat, aes(x = x, y = acl, color = source)) +
  geom_line() +
  facet_grid(axis~location) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 0.3) +
  ylab("Autocorrelation Function") +
  xlab("Time Lag") +
  scale_x_continuous(expand = c(0,0), 
                     breaks = c(0, 0.25, 0.5, 0.75, 1),
                     labels=c("0", "0.25", "0.5", "0.75", "1")) +
  theme_bw(base_size = 12) +
  theme(legend.position = "bottom") +
  scale_color_manual(name = "", values = col_vals[c(3, 1, 2)], 
                     labels = c("Data", "Residuals of Model Fit",
                                "Residuals of Sensitivity Analysis"))

```


